### 2020-05-21 papers-vol-2.tex
Fix margins on first few pages
Don't add the "Part I" in volumes II and III
Fix author's position in author index
Fix compilation error

\part{Regular papers}

@@

\insertmydocument{chapter}{Relationships between Narrative and Argumentation. In Defence of a Functional Account}{Guillermo Sierra Catal\'{a}n}{pdfs/regular/19regularSierraCatalan.docx.pdf} % 19

@@

\insertmydocument{chapter}{Appeals to Popularity: Roles and Functions of ‘Everyone knows X’}{Thierry Herman}{pdfs/regular/48regularHerman.docx.pdf} % 48

@@

\insertmydocument{chapter}{"If You Are A Scientist You Cannot Stop Such A Thing": Scientific Assent and Dissent in the Manhattan Project}{David Erland Isaksen}{pdfs/regular/54regularIsaksen.doc.pdf} % 54

>>>>

\addcontentsline{toc}{part}{Regular papers}
\part*{Regular papers}

@@

\insertmydocument{chapter}{Relationships between Narrative and Argumentation. In Defence of a Functional Account}{Guillermo Sierra~Catal\'{a}n}{pdfs/regular/19regularSierraCatalan.docx.pdf} % 19

@@

\insertmydocument{chapter}{Appeals to Popularity: Roles and Functions of `Everyone knows X'}{Thierry Herman}{pdfs/regular/48regularHerman.docx.pdf} % 48

@@

\insertmydocument{chapter}{"If You Are A Scientist You Cannot Stop Such A Thing": Scientific Assent and Dissent in the Manhattan Project}{David Erland Isaksen}{pdfs/regular/54regularIsaksen.docx.pdf} % 54
